### 2014-01-07 msc-thesis/chapters/2/sec-impact.tex
Added in study conclusions.

>>>>

\section{Related Work}
Although there is an abundance of awareness tools developed in research
today, only a handful have made an attempt to examine indirect conflicts.
Here, I will outline four of the forefront projects in indirect conflicts
and how these projects have influenced the decision making process in
the design and implementation of \textit{Impact}.

I first start with both Codebook~\cite{Begel:2010:CDE} and 
Ariadne~\cite{Trainer:2005:BGT}. These projects produce an exploratory
environment for developers to handle indirect conflicts. Exploratory
pertains to the ability to solve self determined conflicts, meaning that
once a developer discovers a conflict, they can use the tool as a type of
lookup table to solve their issue. Codebook is a type of social developer
network that relates developers to source code, issue repositories and
other social media while Ariadne only looks at source code for developer
to source code association. Through Codebook, developers become
owners of source code artifacts. Both projects also use program 
dependency graphs~\cite{Horwitz:1992:UPD}
in order to relate technical artifacts to each other. These projects make 
use of method call graphs in order to 
determine which methods invoke others which forms the basis for 
linking source code artifacts creating a directed graph. While these 
projects can be great tools 
for solving indirect conflicts which may arise, by querying such directed
graphs to view impacts of conflict creating code, they lack the ability to
detect potential conflicts on their own.

A serious attempt at both detecting and informing developers of
indirect conflicts is the tool Palantir~\cite{Sarma:2007:TSA}. Palantir
monitors developers activities in files with regards to class signatures.
Once a developer changes the signature of a class, such as by modifying changes
in name, parameters, or return values of public methods, any workspace
of other developers which are using that class will be notified. Palantir utilizes
a push-based event model~\cite{Fitzpatrick:2002:SPA} which seems to be
a favored collection system among awareness tools. Sarma et al.
~\cite{Sarma:2007:TSA} also
developed a generic design for future indirect conflict awareness tools. 
However, Palantir falls short in its collection and distribution
mechanisms. First, Palantir only considers ``outside'' appearance of technical
objects, being their return types, parameters, etc. Secondly, Palantir 
only delivers
detected conflicts to developers who are presently viewing or editing
the indirect object while other developers who have used the modified 
class previously are not notified.

I will lastly examine the tool CASI~\cite{Servant:2010:CPI} which uses
a sphere of influence for each developer to determine how source code
changes are indirectly related to other components of a software project.
CASI uses dependency slicing~\cite{Bajracharya:2009:SIS} instead of the 
call graphs in Ariadne~\cite{Trainer:2005:BGT} which gives dependencies among
all source code entities. This provides a verbose output of dependencies when
source code is changed. CASI also implements a visualization where
a developer can see what parts of a software projects he or she may be effecting
with the source code change. This allows the developer themselves to go and fix
potential issues elsewhere in the project before the code change is committed
to the software repository. While CASI covers great ground in its approach,
it still leaves the issue of information overload, although attempts were made
to solve this by having severity levels of indirect conflicts presented to
the user.

### 2014-01-07 msc-thesis/chapters/3/sec-apie.tex
Added in study conclusions.

@@

In this study, I have conducted a case study of 10 open source Java software projects in order to study their change trends surrounding
major releases as previous studies have shown that indirect conflicts occur less at a major release and more so after a major release
or as the beginning of a development cycle. I have presented here 9 major change trends which surround major releases in the open source
projects studied. The 4 change trends found in this study occurring before major releases are: added private classes, 
changed test method signatures, changed documentation, and removed test classes.
The 5 change trends found in this paper occurring after major release are: added test methods, changed test classes, removed public methods, removed
private classes, and removed private methods.

>>>>

\section{Related Work}
\label{sec:rel}
While very little has been published about release quality studies and stability (especially in regards to
indirect conflicts), there have been a few studies which attempt to address the issues directly
or indirectly. Wu et al.~\cite{Wu:2008:QAF} performed a case study of SoftPM, a widely adopted project management tool, to explore the relationships of
pre-release and post-release failures at major releases. Wu et al. found that the ratio of post-release failures to pre-release failures is significantly low
and can be used to show reliability and stability. Hindle et al.~\cite{Hindle:2007:RPD} performed a case study on MySQL which observed a project's behavior
around major and minor release by monitoring artifact check-ins and changes. They found that there are temporary stoppages for source revisions around releases,
indicating that a temporary freeze is taking place for developers and that last minute fixes and manual testing may be performed.
Zaidman et al.~\cite{Zaidman:2011:SCP}, in comparison, studied the co-evolution of production and test code with inspections and analysis
at major and minor releases, showing how test and production code can evolve at different rates and times. These results show that production
and test code should be handled as different cases for a stability measure around major releases.

The study of open source projects revolving around release points has become more accessible by the work of Tsay et al~\cite{Tsay:2011:EMO}. Tsay et al. created
a resource of historical release dates for open source software projects to be used for future studies by other researchers.

In terms of software stability, development techniques have been proposed to increase software stability. 
Fayad~\cite{Fayad:2001:TOI}~\cite{Fayad:2002:ASS} suggests that ``business objects'' (BOs) do not change in nature and that they are inherently stable. These
objects only need to change to accommodate external modules at the interface. Some studies such as Chow et al.~\cite{Chow:2011:SJI} have investigated
the stability of changes to interfaces which are considered a good indication of stability.
Mockus et al.~\cite{Mockus:2008:IQR} used major and minor release points to compare industry process quality to customer-perceived quality of the software
project. Mockus et al. found that defect density is lowest at major releases but at the same time software quality is at its lowest all when compared to minor
releases. The low software quality here relates to end-user errors of installations and configurations. Wermelinger et al.~\cite{Wermelinger:2008:AEE}
showed that stable core architectures can be detected by using source code changes. Finally, Fayad et al.~\cite{Fayad:2010:SSM} have
investigated the Software Stability Model (SSM) for Software Product Lines to show that the SSM's impact on architecture and design of a software product
can help improve the life of the product line and make it more adaptable and applicable.

@@

In this study, I have conducted a case study of 10 open source Java software projects in order to study their change trends surrounding
major releases as previous studies have shown that indirect conflicts occur less at a major release and more so after a major release
or at the beginning of a development cycle. I have presented here 9 major change trends which surround major releases in the open source
projects studied. The 4 change trends found in this study occurring before major releases are: added private classes, 
changed test method signatures, changed documentation, and removed test classes.
The 5 change trends found in this paper occurring after major release are: added test methods, changed test classes, removed public methods, removed
private classes, and removed private methods.

### 2014-01-07 msc-thesis/chapters/3/sec-iced.tex
Added in study conclusions.

>>>>

\section{Related Work}
\label{sec:iced-related}

Since this paper has covered a wide spectrum in regards to indirect conflicts (prevention, detection, resolution, process, and tools), there
exists a large body of work in which to draw from regarding indirect conflicts. While some of the previous literature may not deal explicitly
in the notion of indirect conflicts, lessons learned from topics in awareness, direct conflict detection, and debugging are presented.

Many indirect conflict tools have been created, tested, and published. Sarma et al.~\cite{Sarma:2007:TSA} created Palantir, 
which can both detect potential indirect conflicts, at the class signature level, and alert developers to these conflicts. 
Palantir represented one of the first serious attempts at aiding developers towards indirect conflicts. Holmes et 
al.~\cite{Holmes:2010:CAR} take it one step further with their tool YooHoo, by detecting fine grained source code changes, 
such as method return type changes, and create a taxonomy for different types of changes and their proneness to cause 
indirect conflicts. This tool and its taxonomy had a severely reduced false positive rate, however, the true positives 
detected may already be detectable by current tools such as compilers and unit testing. The tool Ariadne~\cite{Trainer:2005:BGT} 
creates an environment where developers can see how source code changes will affect other areas of a project at the 
method level, using method call graphs, showing where indirect conflicts may occur. This type of exploratory design has 
been used often in the visualization of indirect conflict tools, allowing developers a type of search area for their development
needs. Another indirect conflict tool, CASI~\cite{Servant:2010:CPI}, utilizes dependency slicing~\cite{Bajracharya:2009:SIS} 
instead of method call graphs to provide an environment to see what areas of a project are being affected by a source code change. 
Most of these tools have all shown to have the same common difficulties of scalability, false positives, and information overload, 
which were explored in this paper. Our own tool 
Impact!~\footnote{University of Victoria Computer Science Technical Paper: DCS-351-IR} also suffered these same fates.

Since Cataldo et al.~\cite{Cataldo:2006:ICR} have shown that socio-technical congruence can be leveraged to improve task completion
times, many indirect conflict tools support the idea of a socio-technical congruence~\cite{Kwan:2011:ESC} in order to help
developers solve their indirect conflict issues through social means~\cite{Begel:2010:CDE}~\cite{Borici:2012:CHA}. 
Begel et al.~\cite{Begel:2010:CDE} created Codebook, a type of social developer network related directly to source code
artifacts, which can be used to identify developers and expert knowledge of the code base. Borici et al.~\cite{Borici:2012:CHA}
created ProxiScientia which used technical dependencies between developers to create a network of coordination needs.
Socio-technical congruence however, is largely unproven in regards to its correlation to
software quality~\cite{Kwan:2011:SCE} and again the problems of scalability and information overload become a factor.

For developer interest in regards to software modifications, Kim~\cite{Kim:2011:ESA} found that developers wanted to know whose 
recent code changes semantically interfere with their own code changes, and whether their code is impacted by a code change.
Kim conducted several focus groups as well as web surveys to determine these results. These areas of interest resonate with what was
found in this paper. Developers want to know when a code change is going to interfere with their work in a potentially negative way and
require action on the developer's half.  Kim
also found that developers are concerned with interfaces of objects and when those interfaces change, similar to the object contracts that
were found in this paper. Finally, Kim also identified the same issues towards information overload through false positives with developers
noting ``I get a big laundry list... I see the email and I delete it''.

In a case study of impact awareness, de Souza et. al.~\cite{deSouza:2008:ESS} found that developers use their personal knowledge of the
code base to determine the impact of their code changes on fellow developers, teams, and projects. This corresponds with the findings of
preventative measures we have found in that some human interaction or knowledge is required in preventing indirect conflicts along with
development processes.

In a study regarding static analysis tools, Johnson et. al~\cite{Johnson:2013:WDS} found similar conclusions towards the
ill fit of current static analysis to current development practices. Not being designed properly to fit current development work
flow, and the over abundance of false positives were shown to be factors of developer non-use.

Hattori et. al.~\cite{Hattori:2012:ICG} found, through qualitative user studies, that developers tend to use the bare amount of communication
towards other developers in order to solve direct conflicts, and take the same approach of only communicating once a conflict has arose. This
resonates with ``I work until something breaks''. Hattori et. al. also show that with direct conflicts, the
sooner preemptive information if available to developers the more they will communicate and either avoid or easily solve their code merges.
This is the situation many indirect conflict tools have strived for. In terms of communication, Bolici et. al~\cite{Bolici:2009} give the 
possibility of developer stigmergy as the reason that developers do not need to explicitly communicate with each other about issues. The idea
that developers use artifacts left behind by other developers to solve their issues could play a large role in a lack of formal communication.
Blincoe et al.~\cite{Blincoe:2013:UCC} also found, through data mining techniques, a subset of events related to awareness 
which occur that developers will communicate about as opposed to all awareness events. This again confirms our understanding that developers
only care about certain events which require some action on their part.

While not specifically developed with indirect conflicts in mind, Zeller's delta debugging techniques~\cite{Zeller:2005:WPF}, 
can be applied to solving indirect conflict issues. Zeller gives automated techniques for identifying failure-inducing
changes (as well as other failure causing components) of the software project in order to isolate and debug some issue. These practices fit
with the idea that developers wait for something to go wrong, then wish to fix the issue as fast as possible. Program slicing~\cite{Xu:2005:BSP}
has also been extensively studied in order to aid in debugging in manual or automated techniques.

### 2014-01-07 msc-thesis/chapters/4/chapter-discussion.tex
Added in study conclusions.

As we have seen, indirect conflicts are found to be quite a serious problem that occur frequently,
sporadically, and differ greatly from case to case. These conditions pose large issues for the creation of generalizable theories
or tools in regards to indirect conflicts. These underlying complexities are the probable cause of disinterest of software developers
to proposed or implemented tools as discussed in Section~\ref{sec:review}. This inability to generalize is what I believe to be the
leading cause of information overload and false positives in the awareness system, causing developers to eventually ignore 
information being presented to them, rendering the system useless. These false positives are caused by a difference in what
developers consider to be false positives versus what awareness literature considers they are. This disjoint, as will
be seen, is caused by developers only considering events which cause some action to be taken on their part, to be true positives,
where as current awareness understanding would state any event which is related to an individual's 
work~\cite{Herbsleb06collaborationin}~\cite{Cataldo:2008:SCF}, to be true positives.
``You need a good understanding of what the code change is or else you will have a lot of false positives'' said one developer,
showing that not all changes around an object should be reported for awareness.

>>>>

As we have seen, indirect conflicts are found to be quite a serious problem that occur frequently,
sporadically, and differ greatly from case to case. These conditions pose large issues for the creation of generalizable theories
or tools in regards to indirect conflicts. These underlying complexities are the probable cause of disinterest of software developers
to proposed or implemented tools as discussed in Section~\ref{sec:iced-related}. This inability to generalize is what I believe to be the
leading cause of information overload and false positives in the awareness system, causing developers to eventually ignore 
information being presented to them, rendering the system useless. These false positives are caused by a difference in what
developers consider to be false positives versus what awareness literature considers they are. This disjoint, as will
be seen, is caused by developers only considering events which cause some action to be taken on their part, to be true positives,
where as current awareness understanding would state any event which is related to an individual's 
work~\cite{Herbsleb06collaborationin}~\cite{Cataldo:2008:SCF}, to be true positives.
``You need a good understanding of what the code change is or else you will have a lot of false positives'' said one developer,
showing that not all changes around an object should be reported for awareness.
